Renal IV

### 2017-06-01 renal4.rmd
added hsr
added template for short case
updated sc1

@@

>>>>

# Quiz

-  Clavulanic acid contains beta-lactam, gets preferentially broken down by resistant bacteria. Therefore penicillin and cephalosporins can have an effect.
-  Receptors
    -  M~3~: ACh from parasympathetic pelvic nerve to contract detrusor
    -  B~3~: hypogastric N (sym): noradrenaline relaxation of detrusor
    -  $\alpha_{1}$ in the int sphincter: hypogastric N: contraction of ext sphincter
    -  Nicotinic in the ext sphincter: somatic from pudendal nerve to contract it
    -  Also sensory N AFFERENT in detrusor that is stimulated when bladder is stretched

@@

# Short case 1

> 18F severe burning pain on urination. Offensive urine = smelly. Sexually active. No fever, sweats, nausea, or back pain.

Organ systems involved = {urinary system, reproductive}

Sexual Hx: STI, pregnancy, infn. Facilitates trauma for bugs.

Absence of systemic symptoms $\rightarrow$ localised: not urosepsis, pelvic inflammatory disease (sepsis within the abdomen)

Well person Ix: don't really have to FBC since there is no education that there is systemic effects.

## Trigger 2

Sensitivity and specificity of dipstick: low for both

Empirical treatment: don't want disease progression, also provide some relief from symptoms (stinging during urination due to acidity of urine and also infn+inflammation)

Trimethoprim: works most of the time for *E. coli*, low side effects, generally well tolerated (low allergies)

Antibiotic selection = {narrow spectrum, lowest dose, shortest time}

Medication: empaglutlozin blocks the SGLT-2 transporter so can't reabsorb sugar. Makes people piss out 80g urine, helpful for diabetes, obese, bacteria in urine (increased risk of UTIs).

# Short case 2
